\vspace{-0.7em}
\begin{section}{Research Experience}

    \begin{subsectionnobullet1}{1. Project Research Assistant}{Supervisor - \href{https://www.phy.iitb.ac.in/en/content/varun-bhalerao}{Prof. Varun Bhalerao} (href{https://www.star-iitb.in/}{STAR Lab})}{\textit{Jan 2023 - Present}}{\textit{IIT Bombay, India}}{}

        \vspace{-0.5em}

        % Thermonuclear Bursts Section
        \textbf{\textit{``Thermonuclear Bursts in X-ray Binaries"}}
        \vspace{-0.5em}
        \begin{itemize}
            \item Studying a sample of 15 thermonuclear X-ray Bursts from two transient Low Mass X-ray Binary sources 4U\:1728--34 \& 4U\:1735--44 using \textit{AstroSat} data.
            \vspace{-0.5em}
            \item Developed pipelines for basic data reduction, time-resolved burst spectral analysis, and timing analysis for exploring accretion phenomena and rapid variability in lightcurves.
        \end{itemize}
        \vspace{-0.5em}
        % GROWTH-India Section
        \textbf{\textit{``Fast Transients with GROWTH-India"}}
        \vspace{-0.5em}
        \begin{itemize}
            \item Observations and Follow-up campaigns for Gravitational Wave (GW) events from LIGO, Virgo, KAGRA (LVK) collaborations and fast transients using the 0.7m GROWTH-India telescope in collaboration with the Zwicky Transient Facility (ZTF) led by Caltech. 
            \vspace{-0.5em}
            \item Following up transient X-ray binaries undergoing outbursts.
            \vspace{-0.5em}
            \item Daily scanning for fast transients in ZTF data through \texttt{ZTFRest}.
        \end{itemize}
        
    \end{subsectionnobullet1}

    \vspace{-0.5em}


    \begin{subsectionnobullet1}{2. Vistitng Student Researcher}{Supervisor - \href{https://www.iiap.res.in/people/profile/academic/santanu-mondal/}{Dr. Santanu Mondal}}{\textit{Dec 2022- Jan 2023}}{\textit{IIA Bengaluru, India}}{}
        \vspace{-0.5em}

        \textbf{\textit{``Temporal study of GX 339-4, a Black Hole Transient"}}
        \vspace{-0.5em}
        \begin{itemize}
            \item Conducted energy-dependent time-averaged temporal analysis of a transient black hole X-ray binary GX 339-4 by utilising archival data from \textit{NICER} and \textit{AstroSat} missions.
            \vspace{-0.5em}
            \item Studied energy dependence and time evolution of Quasi periodic Oscillations (QPOs) and their harmonic components in the power density spectrum. 
            \vspace{-0.5em}
            \item Developed pipelines energy dependent and time resolved temporal studies of persistent surces. 
            \vspace{-0.5em}
            \item \textit{Recipient of \textbf{\href{https://www.iiap.res.in/opportunities/visiting-students/internships/}{IIA Visiting Students Fellowship}} (2022)}, Indian Institute of Astrophysics, Bangalore.
        \end{itemize}

    \end{subsectionnobullet1}
    

\end{section}
