\begin{section}{Publications}
    Below is the list of my published/to be submitted refereed publications
    \vspace{-0.3em}
    \begin{enumerate}
        \item \me., et al. (\textit{in prep}) (2024), {``Spectro-Temporal studies of Thermonuclear bursts and kHz QPOs in Slow Burster 4U 1728-34"} \textit{(submitting to ApJ)}
        \vspace{-0.2em}

        \item Mondal, S., \me., et al. (2023), {``Evolution of low-frequency quasi-periodic oscillations in GX 339-4 during its 2021 outburst using AstroSat data"}, \href{https://ui.adsabs.harvard.edu/link_gateway/2023MNRAS.526.4718M/doi:10.1093/mnras/stad3079}{MNRAS}, 526, 4718. (Citations: 2) {\href{https://doi.org/10.1093/mnras/stad3079}{DOI}} (Citations: 4)
        \vspace{-0.2em}

        \item Ahumada, T., Anand, S., Coughlin, M. W., ..... \me ., et al. (2024),{``Searching for gravitational wave optical counterparts with the Zwicky Transient Facility: summary of O4a"}, \href{https://arxiv.org/pdf/2405.12403}{arXiv:2405.12403}, \textit{(Submitted to ApJ)}. (Citations: 3)
        \vspace{-0.2em}

        \item Rekhi. P ., \me., et al. (\textit{in prep}) (2024), {``Timing and spectral studies of 4U 1735-44 using AstroSat"} \textit{(submitting to ApJ)}
        \vspace{-0.2em}
    \end{enumerate}

    Some of my important non-refereed publications are listed below. \href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=AND&filter_database_fq_database=database%3A%22astronomy%22&filter_property_fq_property=AND&filter_property_fq_property=property%3A%22notrefereed%22&fq=%7B!type%3Daqp%20v%3D%24fq_database%7D&fq=%7B!type%3Daqp%20v%3D%24fq_property%7D&fq_database=(database%3A%22astronomy%22)&fq_property=(property%3A%22notrefereed%22)&p_=0&q=Anirudh%20Salgundi&sort=date%20desc%2C%20bibcode%20desc}{\textbf{\underline{\textcolor{navyblue}{Here}}}} is a full list of my non-refereed publications (43 GCNs, 3 TNS and 2 ATels)

    \begin{enumerate}
        \item \me., Swain, V., Kumar, H., et al. (2023), GRB Coordinates Network, {``GRB 230812B: Zwicky Transient Facility Identifies Optical Afterglow Candidate of Fermi GRB (Trigger 713559497)"}, \href{https://gcn.nasa.gov/circulars/34397}{34397, 1.}
        \vspace{-0.2em}

        \item \me., Swain, V., Kumar, R., et al. (2023), GRB Coordinates Network, {``AT2023sva/GRB230916B: GIT observations of the afterglow"}, \href{https://gcn.nasa.gov/circulars/34780}{34780, 1.}
        
        \vspace{-0.2em}
        
        % \item Pathak, U., \me., Waratkar, G., et al. (2023), GRB Coordinates Network, {``GRB 230812B: Chandra late-time detection of the X-ray afterglow"}, \href{https://gcn.nasa.gov/circulars/34632}{34632, 1.}
        
        % \vspace{-0.2em}

        \item Swain, V., Andreoni, I., Coughlin, M., Kumar, H., \me., (2023), Transient Name Server AstroNote, {``ZTF23aaoohpy\/AT2023lcr: Zwicky Transient Facility discovery of a fast fading red transient"}, \href{https://www.wis-tns.org/astronotes/astronote/2023-178}{Transient Name Server 178, 1.}
        
        \vspace{-0.2em}

        \item Thomas, N. T., \textbf{Anirudh, S}., Giridharan, L., Gudennavar, S. B., et al. (2022), The Astronomer's Telegram, {``AstroSat observes XTE J1701-462 in its Z phase"}, \href{https://www.astronomerstelegram.org/?read=15654}{15654, 1.}
    \end{enumerate}

\end{section}
