\small
Up--to--date list can be found at: 
\faGlobe~\href{https://ui.adsabs.harvard.edu/search/q=orcid%3A0000-0003-3173-4691&sort=date+desc}{NASA ADS Library} \& \faIcon{google}~\href{https://scholar.google.com/citations?user=BdMzZJ4AAAAJ}{Google Scholar}, 
\\
\vspace{0.5em}
\normalsize

\textit{\textbf{Below is the list of refereed publications I am a part of:}}
\begin{enumerate}
\item Srinivasaragavan, G. P., Perley, D. A., Ho, A. Y. Q., O'Connor, B., de Ugarte Postigo, A.,  (includes \me) ., et al. (2025), \mnras, {``Multiwavelength analysis of AT 2023sva: a luminous orphan afterglow with evidence for a structured jet"}, 538, 351.

\item \me, Bala, S., Raman, G., Pathak, U., \& Bhalerao, V. (2024), arXiv e-prints, {``"Bursts, Beats, and Beyond": Uncovering the landscape from accretion to ignition of 4U 1728-34 using AstroSat"}, arXiv:2412.06644.

\item Ahumada, T., Anand, S., Coughlin, M. W., Gupta, V., Kasliwal, M. M., (includes \me)., et al. (2024), \pasp, {``Searching for Gravitational Wave Optical Counterparts with the Zwicky Transient Facility: Summary of O4a"}, 136, 114201.

\item Mondal, S., \me, Chatterjee, D., Jana, A., Chang, H.-K., et al. (2023), \mnras, {``Evolution of low-frequency quasi-periodic oscillations in GX 339-4 during its 2021 outburst using AstroSat data"}, 526, 4718.

\end{enumerate}

\textit{\textbf{Below is the list of Non-refereed publications (GCNs, ATels, TNS) that I am a part of:}}

\begin{enumerate}
\item Eappachen, D., Swain, V., \me, Sahu, D. K., Saikia, A. P., et al. (2025), GRB Coordinates Network, {``EP250427a/GRB250427A: HCT optical follow-up"}, 40289, 1.

\item \me, Swain, V., Eappachen, D., Saikia, A. P., Bhalerao, V., et al. (2025), GRB Coordinates Network, {``EP250428b: GROWTH-India telescope optical upper limit"}, 40284, 1.

\item Swain, V., \me, Wagh, Y., Saikia, A. P., Eappachen, D., et al. (2025), GRB Coordinates Network, {``GRB250427A/EP250427a GIT optical afterglow detection:"}, 40270, 1.

\item Mohan, T., Swain, V., \me, Kumar, R., Bhalerao, V., et al. (2024), GRB Coordinates Network, {``GRB 240529A: GROWTH-India optical follow-up"}, 36576, 1.

\item Ahumada, T., Stein, R., Swain, V., \me, Suresh, A., et al. (2024), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S240422ed: Zwicky Transient Facility contuinued observations of S240422ed and candidate analysis"}, 36310, 1.

\item Swain, V., Waratkar, G., \me, Kumar, R., Suresh, A., et al. (2024), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S240422ed: 2.5m PRL Telescope follow-up of the Swift/XRT source S240422ed\_X190"}, 36305, 1.

\item Swain, V., Waratkar, G., Pathak, U., \me, Suresh, A., et al. (2024), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S240422ed: Himalayan Chandra Telescope follow-up of the Swift/XRT source S240422ed\_X101"}, 36287, 1.

\item Ahumada, T., Anand, S., Karambelkar, V., Bellm, E., Stein, R., et al. (includes \me) (2024), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S240422ed: Zwicky Transient Facility observations and candidates"}, 36246, 1.

\item Swain, V., Pathak, U., Karambelkar, V., Jegou Du Laz, T., Ahumada, T., (includes \me) et al. (2024), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S240413p: Zwicky Transient Facility observations"}, 36080, 1.

\item Wagh, Y., Kumar, R., Swain, V., \me, Bhalerao, V., et al. (2023), GRB Coordinates Network, {``GRB 231215A: GROWTH-India optical follow-up"}, 35354, 1.

\item Kumar, R., \me, Swain, V., Wagh, Y., Bhalerao, V., et al. (2023), Transient Name Server Discovery Report, {``GIT Transient Discovery Report for 2023-11-15"}, 2023-2965, 1.

\item Kumar, R., \me, Swain, V., Bhalerao, V., Anupama, G. C., et al. (2023), GRB Coordinates Network, {``GRB 231117A: GIT optical follow-up"}, 35089, 1.

\item Kumar, R., Karambelkar, V., Swain, V., Bhalerao, V., \me, et al. (2023), GRB Coordinates Network, {``GRB 231115A / AT2023xvj: Updated GIT analysis"}, 35055, 1.

\item Kumar, R., \me, Swain, V., Wagh, Y., Bhalerao, V., et al. (2023), GRB Coordinates Network, {``GRB 231115A: GROWTH-India discovery of a potential optical counterpart"}, 35041, 1.

\item Ahumada, T., \me, Stein, R., Karambelkar, V., Waratkar, G., et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S231113bw: Zwicky Transient Facility observations"}, 35032, 1.

\item Kumar, R., \me, Sharma, R., Waratkar, G., Suresh, A., et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S231113bw: GROWTH-India coverage and upper limits"}, 35027, 1.

\item Kumar, R., \me, Swain, V., Bhalerao, V., Barway, S., et al. (2023), GRB Coordinates Network, {``GRB231111A: GIT confirmation of the optical afterglow"}, 34984, 1.

\item Ahumada, T., Swain, V., \me, Karambelkar, V., Waratkar, G., et al. (2023), GRB Coordinates Network, {``GRB 231012A: Zwicky Transient Facility Follow-Up of a Fermi Short GRB (Trigger 705709044)"}, 34855, 1.

\item Kumar, R., Wagh, Y., Sharma, R., \me, Swain, V., et al. (2023), GRB Coordinates Network, {``GRB 231018A: GROWTH-India Follow-Up of a Fermi Long GRB"}, 34839, 1.

\item Kumar, R., \me, Sharma, R., Wagh, Y., Swain, V., et al. (2023), GRB Coordinates Network, {``GRB231017A: GROWTH-India upper limits on the optical afterglow"}, 34833, 1.

\item \me, Swain, V., Kumar, R., Waratkar, G., Sharma, R., et al. (2023), GRB Coordinates Network, {``AT2023sva / GRB230916B: GIT observations of the afterglow"}, 34780, 1.

\item Ahumada, T., Swain, V., Anand, S., Stein, R., Karambelkar, V., (includes \me) et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230917af: Zwicky Transient Facility observations"}, 34755, 1.

\item Pathak, U., \me, Waratkar, G., Swain, V., Bhalerao, V., et al. (2023), GRB Coordinates Network, {``GRB 230812B: Chandra late-time detection of the X-ray afterglow"}, 34632, 1.

\item Li, M. L., Vail, J. L., Ho, A. Y. Q., Coughlin, M., Perley, D., (includes \me) et al. (2023), Transient Name Server AstroNote, {``ZTF Observations of the Candidate Optical Afterglow AT 2023qxj"}, 238, 1.

\item Swain, V., \me, Kumar, R., Sharma, R., Kumar, H., et al. (2023), GRB Coordinates Network, {``GRB 230827.256 : GIT optical follow-up of ZTF23abaanxz/AT2023qxj"}, 34576, 1.

\item Li, M. L., Vail, J. L., Ho, A. Y. Q., Coughlin, M., Perley, D., (includes \me) et al. (2023), GRB Coordinates Network, {``AT 2023qxj: ZTF discovery of the likely afterglow of Fermi GRB 230827256"}, 34574, 1.

\item Kumar, R., \me, Swain, V., Kumar, H., Bhalerao, V., et al. (2023), GRB Coordinates Network, {``GRB 20230818A: GIT optical upper limit"}, 34514, 1.

\item Kumar, H., Swain, V., Teja, R., Kumar, R., \me, et al. (2023), GRB Coordinates Network, {``GRB 230812B: GIT Confirmation of SN rise"}, 34500, 1.

\item Kumar, R., Sharma, R., Swain, V., \me, Kumar, H., et al. (2023), GRB Coordinates Network, {``GRB230816A: Possible host and GIT detection of optical counterpart"}, 34460, 1.

\item Kumar, R., \me, Swain, V., Kumar, H., Bhalerao, V., et al. (2023), GRB Coordinates Network, {``GRB 230812B: GIT optical follow-up"}, 34420, 1.

\item \me, Swain, V., Kumar, H., Ahumada, T., Stein, R., et al. (2023), GRB Coordinates Network, {``GRB 230812B: Zwicky Transient Facility Identifies Optical Afterglow Candidate of a Fermi GRB (Trigger 713559497)"}, 34397, 1.

\item Swain, V., Andreoni, I., Coughlin, M., Kumar, H., \& \me (2023), Transient Name Server AstroNote, {``ZTF23aaoohpy/AT2023lcr: Zwicky Transient Facility discovery of a fast fading red transient"}, 178, 1.

\item Reusch, S., Ahumada, T., \me, Srinivasaragavan, G., Coughlin, M., et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230516az: GOTO candidate counterpart GOTO23hu ruled out by Zwicky Transient Facility observations"}, 34103, 1.

\item Ahumada, T., Andreoni, I., Anumarlapudi, A., Karambelkar, V., Kumar, H., (includes \me) et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230627c: Additional observations from the Zwicky Transient Facility"}, 34100, 1.

\item Anumarlapudi, A., Ahumada, T., Kasliwal, M., Karambelkar, . 34089iraj ., Kumar, H., (includes \me) et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230627c: Zwicky Transient Facility observations and candidates"}, 34089, 1.

\item Kumar, H., Swain, V., \me, Bhalerao, V., Anupama, G. C., et al. (2023), GRB Coordinates Network, {``ZTF23aaoohpy/AT2023lcr: GROWTH-India Telescope follow-up observations"}, 34025, 1.

\item Swain, V., Andreoni, I., Coughlin, M., Kumar, H., \me, et al. (2023), GRB Coordinates Network, {``ZTF23aaoohpy/AT2023lcr: Zwicky Transient Facility discovery of a fast fading red transient"}, 34022, 1.

\item Kumar, H., Swain, V., \me, Angail, K., Bhalerao, V., et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230615az: GROWTH-India candidates"}, 33974, 1.

\item Ahumada, T., Waratkar, G., Karambelkar, V., Stein, R., \me, et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230602ap: Zwicky Transient Facility observations"}, 33929, 1.

\item Karambelkar, V., Ahumada, T., Stein, R., Anumarlapudi, A., Waratkar, G.,  (includes \me) et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230529ay: Zwicky Transient Facility observations"}, 33900, 1.

\item Ahumada, T., Anumarlapudi, A., Karambelkar, V., Stein, R., Waratkar, G., (includes \me) et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230528a: Zwicky Transient Facility observations"}, 33899, 1.

\item Anumarlapudi, A., Ahumada, T., Karambelkar, V., Stein, R., Waratkar, G., .(includes \me) et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230527ch: Zwicky Transient Facility observations"}, 33898, 1.

\item Swain, V., Kumar, H., Karambelkar, V., \me, Anumarlapudi, A., et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230521k: Additional candidates from Zwicky Transient Facility"}, 33858, 1.

\item Ahumada, T., Karambelkar, V., Stein, R., Waratkar, G., \me, et al. (2023), GRB Coordinates Network, {``LIGO/Virgo/KAGRA S230521k: Zwicky Transient Facility observations"}, 33848, 1.

\item Ahumada, T., Karambelkar, V., Stein, R., Kumar, H., Swain, V., (includes \me)., et al. (2023), GRB Coordinates Network, {``GRB 230513A: Zwicky Transient Facility continuous observations of a Fermi Short GRB (Trigger 705709044)"}, 33812, 1.

\item Kumar, H., Swain, V., \me, Suresh, A., Ahumada, T., et al. (2023), GRB Coordinates Network, {``GRB 230513A: Zwicky Transient Facility Follow-Up of a Fermi Short GRB (Trigger 705709044)"}, 33801, 1.

\item Swain, V., Kumar, H., \me, Bhalerao, V., Anupama, G. C., et al. (2023), GRB Coordinates Network, {``GRB 230512A: GIT non detection of afterglow candidate"}, 33797, 1.

\item Kumar, H., Swain, V., \me, Bhalerao, V., Anupama, G. C., et al. (2023), GRB Coordinates Network, {``GRB 230512A: GIT optical follow-up ZTF candidates"}, 33786, 1.

\item Swain, V., \me, Kumar, H., Bhalerao, V., Anupama, G. C., et al. (2023), GRB Coordinates Network, {``GRB 230510A: GIT optical upper limits"}, 33777, 1.

\end{enumerate}